Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-05-21 vesicle_code/docs/adhesion/adhesion.tex
improving phase diagrams

\begin{figure}[htp]
  \includegraphics[height=0.27\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
  \includegraphics[height=0.27\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
  \includegraphics[height=0.27\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
  inclination angle of a doublet formed by vesicles of reduced area
  $\Delta A = 0.7$ in an extensional flow with an extensional rate
  $\chi$.  {\em Middle}: The final inclination angle of doublets.  At
  larger extensional rates, the doublet is broken by the flow.  {\em
  Right}: A phase diagram of the long-time behavior of a fluid trap
  formed by two adhering vesicles in an extensional flow.  Results are
  not reported for some of the low extensional rates since the doublet
  had not tilted to an equilibrium inclination angle for the given time
  horizon.}
\end{figure}

@@

\begin{figure}
  \includegraphics[height=0.35\textwidth]{figs/shear_adR4em1Chi1e0_ra-090.pdf}
  \includegraphics[height=0.35\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
  \caption{\label{fig:sflow_phase_diagram} {\em Left}: Distance between
  a pair of vesicles in a planar shear flow with shear rate $\chi=0.5$,
  and separation distance $\delta = 0.4$.  The different lines
  correspond to a linear spacing of Hamaker constants ranging from
  $\mathcal{H}=0.1$ and $\mathcal{H}=1.0$.  {\em Right}: Phase diagram
  of vesicle hydrodynamics in a shear flow.  At a fixed reduced area
  $\Delta A=0.90$ and $\delta = 0.4$, the critical Hamaker constant
  $\mathcal{H}$ for binding of two vesicles in a shear flow depends on
  the shear rate $\chi$.}
\end{figure}

>>>>

\begin{figure}[htp]
  \includegraphics[height=0.26\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
  \includegraphics[height=0.26\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
  \includegraphics[height=0.26\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
  inclination angle of a doublet formed by vesicles of reduced area
  $\Delta A = 0.7$ in an extensional flow with an extensional rate
  $\chi$.  {\em Middle}: The final inclination angle of doublets.  At
  larger extensional rates, the doublet is broken by the flow.  {\em
  Right}: A phase diagram of the long-time behavior of a fluid trap
  formed by two adhering vesicles in an extensional flow.  Results are
  not reported for some of the low extensional rates since the doublet
  had not tilted to an equilibrium inclination angle for the given time
  horizon.}
\end{figure}

@@

\begin{figure}
  \includegraphics[height=0.27\textwidth]{figs/shear_adR4em1Chi1e0_ra-090.pdf}
  \includegraphics[height=0.27\textwidth]{figs/shear_adR4em1_ra090_phaseDiagram.pdf}
  \includegraphics[height=0.27\textwidth]{figs/shear_adR1em1_ra090_phaseDiagram.pdf}
  \caption{\label{fig:sflow_phase_diagram} {\em Left}: Distance between
  a pair of vesicles in a planar shear flow with shear rate $\chi=0.5$,
  and separation distance $\delta = 0.4$.  The different lines
  correspond to a linear spacing of Hamaker constants ranging from
  $\mathcal{H}=0.1$ and $\mathcal{H}=1.0$.  {\em Center and Right}:
  Phase diagram of vesicle hydrodynamics in a shear flow with $\delta =
  0.4$ (center) and $\delta = 0.1$ (right) with reduced area  $\Delta A
  = 0.9$. The critical Hamaker constant $\mathcal{H}$ for binding of two
  vesicles in a shear flow depends on the shear rate $\chi$.  For a
  doublet to form, lower separation distances require a stronger Hamaker
  constants at a given shear rate.}
\end{figure}
